When, why, and how to avoid, prefer, or tolerate inbreeding

### 2018-02-26 presentation/inbreeding.Rmd
Small changes

<script src="https://ajax.googleapis.com/ajax/libs/jquery/3.1.1/jquery.min.js"></script>

<script>
  $(document).ready(function() {
    $('slide:not(.backdrop):not(.title-slide)').append('<div class=\"footnotes\">');

    $('footnote').each(function(index) {
      var text  = $(this).html();
      var fnNum = (index+1).toString().sup();
      $(this).html(text + fnNum);

      var footnote   = fnNum + ': ' + $(this).attr('content') + '<br/>';
      var oldContent = $(this).parents('slide').children('div.footnotes').html();
      var newContent = oldContent + footnote;
      $(this).parents('slide').children('div.footnotes').html(newContent);
    });
  });
</script>

@@

- Inbreeding avoidance is predicted given a sufficiently high threshold of inbreeding depression
- Inbreeding depression thresholds differ between females and males causing sexual conflict
- Females should prefer inbreeding below their inbreeding depression threshold (resource limited) <footnote content="The first awesoem footnote!">here</footnote>:
- Males should *tolerate* inbreeding below their threshold, but *never prefer* (sis will be fine)

>>>>

<script src="https://ajax.googleapis.com/ajax/libs/jquery/3.1.1/jquery.min.js"></script>
<script>
$(document).ready(function() {
  $('slide:not(.backdrop):not(.title-slide)').append('<div class=\"footnotes\">');

  $('footnote').each(function(index) {
    var text  = $(this).html();
    var fnNum = (index+1).toString();
    $(this).html(fnNum.sup());

    var footnote   = fnNum + '. ' + text + '<br/>';
    var oldContent = $(this).parents('slide').children('div.footnotes').html();
    var newContent = oldContent + footnote;
    $(this).parents('slide').children('div.footnotes').html(newContent);
  });
});
</script>

@@

- Inbreeding avoidance is predicted given a sufficiently high threshold of inbreeding depression
- Inbreeding depression thresholds differ between females and males causing sexual conflict
- Females should prefer inbreeding below their inbreeding depression threshold (resource limited)<footnote content="The first awesoem footnote!">here</footnote>:
- Males should *tolerate* inbreeding below their threshold, but *never prefer* (sis will be fine)

## Extensions of Parker's model

## Limitations of this modelling approach

## Individual-based modelling

- Much different assumptions
- See if we can get a similar answer
